### 2023-04-10 main/chapter_theory.tex
begin majorana neutrino bit

>>>>

\subsubsection{Future Majorana-Dirac possibilities}
% TODO deleteme
% • Opportunities for future SMs – include description of experiemental
% expectations for Majorana vs Dirac neutrinos (double-beta decay, accelerator
% neutrino experiments (DUNE, HyperK), reactors etc.
Future experimental results might resolve the nature of neutrinos.
% 0vBB
If neutrinos have a Majorana nature, then nuclear isotopes that naturally
undergo double-beta decay (emitting two electrons and two neutrinos)
cold rarely undergo neutrinoless double-beta decay ($0\nu\beta\beta$).
In $0\nu\beta\beta$ events, the two neutrinos annihilate to leave the electrons
emitted back-to-back without missing momentum.
Current results have not observed $0\nu\beta\beta$ decays, but have set limits
on $0\nu\beta\beta$ lifetimes in excess of $10^{21}\,\mathrm{years}$
for many nuclear isotopes~\cite{Bilenky:2014uka}.
Future experiments, such as SuperNEMO~\cite{Barabash:2011row},
will study $0\nu\beta\beta$ with increased precision.

% accelerator experiments
Large upcoming neutrino experiments,
DUNE~\cite{DUNE:2016hlj} and
Hyper-Kamiokande~\cite{Hyper-Kamiokande:2018ofw},
will use accelerator-produced neutrinos to make precise measurements of the
neutrinos' Dirac CP violation,
their mass ordering, and their flavour oscillations;
although these experiments do not directly probe the neutrinos' possible
Majorana components, they will be indirectly sensitive through possible new
effects~\cite{Carrasco-Martinez:2020mlg}.

% reactors
Modern experiments that detect neutrinos from nuclear reactors,
such as JUNO % ~\cite{TODO},
are not also
\TODO{reactors}
% etc??
\TODO{etc??}

Other approaches to testing neutrinos' Majorana nature are not competitive with
$0\nu\beta\beta$. These proposed alternatives include \TODO{}
% https://link.springer.com/article/10.1007/JHEP01(2019)122
% https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.112.131802
% https://www.sciencedirect.com/science/article/pii/S0370269318310001?via%3Dihub
% https://journals.aps.org/prd/abstract/10.1103/PhysRevD.96.075006
